---
title: "Plant Survival Data Analysis"
author: '490416255'
output:
  html_document:
    code_folding:
    fig_caption: yes
    number_sections: yes
    self_contained: yes
    theme: journal
    toc: yes
    toc_depth: 3
    toc_float: yes
  word_document:
    toc: yes
    toc_depth: '3'
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r include = FALSE}
require(dplyr)
require(ggplot2)
require(readxl)
require(agricolae)
require(emmeans)
require(lattice)
require(lme4)
require(nlme)
require(car)
require(glmmTMB)
require(brms)
require(rms)
require(broom.mixed)
require(multcomp)
require(multcompView)
require(MASS)
require(olsrr)
```

# Survival

```{r}
biomass_data_run1 <- read_xlsx("biomass_data.xlsx", sheet = "Run1")
biomass_data_run2 <- read_xlsx("biomass_data.xlsx", sheet = "Run2")
```

## Comparison between C. virgata Experiments

```{r}
biomass_data_run1_trim <- biomass_data_run1[,-c(1, 2, 4, 6, 10)]
biomass_data_run2_trim <- biomass_data_run2[,-c(1, 2, 4, 6, 8)]
```

Selecting FTR rows

```{r}
biomass_data_run1_FTR <- filter(biomass_data_run1_trim, Species == "FTR")
biomass_data_run2_FTR <- filter(biomass_data_run2_trim, Species == "FTR")
```

Creating survival column

```{r}
biomass_data_run1_FTR_survival <- mutate(biomass_data_run1_FTR, survival = ((Number_surviving_after_28_days/Plant_Number)))

biomass_data_run2_FTR_survival <- mutate(biomass_data_run2_FTR, survival = ((Number_surviving_after_28_days/Plant_Number)))
```

Combining data sets

```{r}
survival_FTR_combine <- bind_rows(biomass_data_run1_FTR_survival, biomass_data_run2_FTR_survival, .id = "id")
```

```{r}
survival_FTR_combine$id <- as.factor(survival_FTR_combine$id) 
survival_FTR_combine$Block <- as.factor(survival_FTR_combine$Block) 
survival_FTR_combine$Treatment <- as.factor(survival_FTR_combine$Treatment) 
```

```{r}
vor_remove <- c("vor", "para/vor") #Remove voraxor involved treatments

survival_FTR_combine_filter <- filter(survival_FTR_combine, !Treatment %in% vor_remove)

glmer.FTR_survival <- glmer(survival ~ id + (1|Block), family = binomial, data = survival_FTR_combine_filter)
summary(glmer.FTR_survival)
```

Can't combine as p < 0.05

## Comparison between S. oleraceus Experiments

Selecting ST rows

```{r}
biomass_data_run1_ST <- filter(biomass_data_run1_trim, Species == "ST")
biomass_data_run2_ST <- filter(biomass_data_run2_trim, Species == "ST")
```

Creating survival column

```{r}
biomass_data_run1_ST_survival <- mutate(biomass_data_run1_ST, survival = ((Number_surviving_after_28_days/Plant_Number)))

biomass_data_run2_ST_survival <- mutate(biomass_data_run2_ST, survival = ((Number_surviving_after_28_days/Plant_Number)))
```

Combining data sets

```{r}
survival_ST_combine <- bind_rows(biomass_data_run1_ST_survival, biomass_data_run2_ST_survival, .id = "id")
```

```{r}
survival_ST_combine$id <- as.factor(survival_ST_combine$id) 
survival_ST_combine$Block <- as.factor(survival_ST_combine$Block) 
survival_ST_combine$Treatment <- as.factor(survival_ST_combine$Treatment) 
```

```{r}
glmer.ST_survival <- glmer(survival ~ id + (1|Block), family = binomial, data = survival_ST_combine)
summary(glmer.ST_survival)
```

Can't combine as p < 0.05

## C. virgata Analysis

### Run 1

Generalised least squares regression

```{r}
biomass_data_run1_FTR_survival <- mutate(biomass_data_run1_FTR_survival, asin_percent_damage = (asin(sqrt(survival))))

biomass_data_run1_FTR_survival <- mutate(biomass_data_run1_FTR_survival, asin_backtrans_percent_damage = ((sin(asin_percent_damage))^2))

gls.FTR_R1_survival_M1 <- gls(asin_percent_damage ~ Treatment + Block, data = biomass_data_run1_FTR_survival)

plot(gls.FTR_R1_survival_M1) # Fanning residuals - model assumptions were not met
```

Backtranformed means

```{r}
avg_asin_FTR_R1_survival <- biomass_data_run1_FTR_survival %>%
  group_by(Treatment) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_sin_FTR_R1_survival <- mutate(avg_asin_FTR_R1_survival, mean_asin_backtrans = ((sin(mean_asin))^2))

avg_sin_FTR_R1_survival
```

### Run 2

```{r}
biomass_data_run2_FTR_survival$Treatment <- as.factor(biomass_data_run2_FTR_survival$Treatment) 
biomass_data_run2_FTR_survival$Block <- as.factor(biomass_data_run2_FTR_survival$Block)
```

```{r}
biomass_data_run2_FTR_survival <- mutate(biomass_data_run2_FTR_survival, asin_percent_damage = (asin(sqrt(survival))))

biomass_data_run2_FTR_survival <- mutate(biomass_data_run2_FTR_survival, asin_backtrans_percent_damage = ((sin(asin_percent_damage))^2))

gls.FTR_R2_survival <- gls(asin_percent_damage ~ Treatment + Block, data = biomass_data_run2_FTR_survival)

plot(gls.FTR_R2_survival)

Anova(gls.FTR_R2_survival)

emm.FTR_R2_Survival <- emmeans(gls.FTR_R2_survival, specs = ~ Treatment)

cld(emm.FTR_R2_Survival) 
```

Backtransformed means

```{r}
avg_asin_FTR_R2_survival <- biomass_data_run2_FTR_survival %>%
  group_by(Treatment) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_sin_FTR_R2_survival <- mutate(avg_asin_FTR_R2_survival, mean_asin_backtrans = ((sin(mean_asin))^2))

avg_sin_FTR_R2_survival
```


## S. oleraceus Analysis

### Run 1

```{r}
biomass_data_run1_ST_survival <- mutate(biomass_data_run1_ST_survival, asin_percent_damage = (asin(sqrt(survival))))

biomass_data_run1_ST_survival <- mutate(biomass_data_run1_ST_survival, asin_backtrans_percent_damage = ((sin(asin_percent_damage))^2))

gls.ST_R1_survival <- gls(asin_percent_damage ~ Treatment + Block, data = biomass_data_run1_ST_survival)

plot(gls.ST_R1_survival)

Anova(gls.ST_R1_survival)

emm.ST_R1_Survival <- emmeans(gls.ST_R1_survival, specs = ~ Treatment)

cld(emm.ST_R1_Survival) 
```

```{r}
avg_asin_ST_R1_survival <- biomass_data_run1_ST_survival %>%
  group_by(Treatment) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_sin_ST_R1_survival <- mutate(avg_asin_ST_R1_survival, mean_asin_backtrans = ((sin(mean_asin))^2))

avg_sin_ST_R1_survival
```

### Run 2

```{r}
biomass_data_run2_ST_survival$Treatment <- as.factor(biomass_data_run2_ST_survival$Treatment) 
biomass_data_run2_ST_survival$Block <- as.factor(biomass_data_run2_ST_survival$Block)
```

```{r}
biomass_data_run2_ST_survival <- mutate(biomass_data_run2_ST_survival, asin_percent_damage = (asin(sqrt(survival))))

biomass_data_run2_ST_survival <- mutate(biomass_data_run2_ST_survival, asin_backtrans_percent_damage = ((sin(asin_percent_damage))^2))

gls.ST_R2_survival <- gls(asin_percent_damage ~ Treatment + Block, data = biomass_data_run2_ST_survival)

plot(gls.ST_R2_survival)

Anova(gls.ST_R2_survival)

emm.ST_R2_Survival <- emmeans(gls.ST_R2_survival, specs = ~ Treatment)

cld(emm.ST_R2_Survival) 
```

```{r}
avg_asin_ST_R2_survival <- biomass_data_run2_ST_survival %>%
  group_by(Treatment) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_sin_ST_R2_survival <- mutate(avg_asin_ST_R2_survival, mean_asin_backtrans = ((sin(mean_asin))^2))
```


## Conyza spp. Analysis

### Run 1

```{r}
biomass_data_run1_FB <- filter(biomass_data_run1_trim, Species == "FB")
biomass_data_run1_FB_survival <- mutate(biomass_data_run1_FB, survival = ((Number_surviving_after_28_days/Plant_Number)))
biomass_data_run1_FB_survival_clean <- biomass_data_run1_FB_survival[complete.cases(biomass_data_run1_FB_survival),]
```

```{r}
biomass_data_run1_FB_survival_clean_asin <- mutate(biomass_data_run1_FB_survival_clean, asin_percent_damage=(asin(sqrt(survival))))

gls.FB_R1_survival <- gls(asin_percent_damage ~ Treatment + Block, data = biomass_data_run1_FB_survival_clean_asin)

plot(gls.FB_R1_survival)

Anova(gls.FB_R1_survival)

emm.FB_R1_Survival <- emmeans(gls.FB_R1_survival, specs = ~ Treatment)

cld(emm.FB_R1_Survival) 
```

```{r}
avg_asin_FB_R1_survival <- biomass_data_run1_FB_survival_clean_asin %>%
  group_by(Treatment) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_sin_FB_R1_survival <- mutate(avg_asin_FB_R1_survival, mean_asin_backtrans = ((sin(mean_asin))^2))

avg_sin_FB_R1_survival
```


### Run 2

```{r}
biomass_data_run2_FB <- filter(biomass_data_run2_trim, Species == "FB")
biomass_data_run2_FB_survival <- mutate(biomass_data_run2_FB, survival = ((Number_surviving_after_28_days/Plant_Number)))
```

```{r}
biomass_data_run2_FB_survival <- mutate(biomass_data_run2_FB_survival, asin_percent_damage = (asin(sqrt(survival))))

gls.FB_R2_survival <- gls(asin_percent_damage ~ Treatment + Block, data = biomass_data_run2_FB_survival)

plot(gls.FB_R2_survival)

Anova(gls.FB_R2_survival)

emm.FB_R2_Survival <- emmeans(gls.FB_R2_survival, specs = ~ Treatment)

cld(emm.FB_R2_Survival) 
```

```{r}
avg_asin_FB_R2_survival <- biomass_data_run2_FB_survival %>%
  group_by(Treatment) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_sin_FB_R2_survival <- mutate(avg_asin_FB_R2_survival, mean_asin_backtrans = ((sin(mean_asin))^2))

avg_sin_FB_R2_survival
```

# Biomass

```{r}
biomass_data_run1 <- read_xlsx("biomass_data.xlsx", sheet = "Run1")
biomass_data_run2 <- read_xlsx("biomass_data.xlsx", sheet = "Run2")
```

## Comparison between C. virgata Experiments

```{r}
biomass_data_run1_trim <- biomass_data_run1[,-c(1, 3, 4, 6)]
biomass_data_run2_trim <- biomass_data_run2[,-c(1, 3, 4, 6, 8)]
```

Selecting FTR rows

```{r}
biomass_data_run1_FTR <- filter(biomass_data_run1_trim, Species == "FTR")
biomass_data_run2_FTR <- filter(biomass_data_run2_trim, Species == "FTR")
```

Creating weight/surviving plants column

```{r}
biomass_data_run1_FTR_weights <- mutate(biomass_data_run1_FTR, weight_per_plant = (Weight/Number_surviving_after_28_days))
biomass_data_run2_FTR_weights <- mutate(biomass_data_run2_FTR, weight_per_plant = (Weight/Number_surviving_after_28_days))
```

Combining data sets (weight/plant)

```{r}
biomass_FTR_combine <- bind_rows(biomass_data_run1_FTR_weights, biomass_data_run2_FTR_weights, .id = "id")
```

NA's = 0

```{r}
biomass_FTR_combine[is.na(biomass_FTR_combine)] = 0
```


T-Test

```{r}
biomass_FTR_combine$id <- as.factor(biomass_FTR_combine$id) 
biomass_FTR_combine$Block <- as.factor(biomass_FTR_combine$Block) 
biomass_FTR_combine$Treatment <- as.factor(biomass_FTR_combine$Treatment) 

vor_remove <- c("vor", "para/vor")

biomass_FTR_combine_filter <- filter(biomass_FTR_combine, !Treatment %in% vor_remove) #Removing voraxor involved treatments

aov.FTR_weights <- aov(weight_per_plant ~ id + Block, data = biomass_FTR_combine)

plot(aov.FTR_weights)

summary(aov.FTR_weights)
```


Can't combine FTR as p < 0.05

## Comparison between S. oleraceus Experiments

Selecting ST rows

```{r}
biomass_data_run1_ST <- filter(biomass_data_run1_trim, Species == "ST")
biomass_data_run2_ST <- filter(biomass_data_run2_trim, Species == "ST")
```

Creating weight/surviving plants column

```{r}
biomass_data_run1_ST_weights <- mutate(biomass_data_run1_ST, weight_per_plant = (Weight/Number_surviving_after_28_days))
biomass_data_run2_ST_weights <- mutate(biomass_data_run2_ST, weight_per_plant = (Weight/Number_surviving_after_28_days))
```

Combining data sets

```{r}
biomass_ST_combine <- bind_rows(biomass_data_run1_ST_weights, biomass_data_run2_ST_weights, .id = "id")
```

NA's = 0

```{r}
biomass_ST_combine[is.na(biomass_ST_combine)] = 0
```


T-Test

```{r}
biomass_ST_combine$id <- as.factor(biomass_ST_combine$id) 
biomass_ST_combine$Block <- as.factor(biomass_ST_combine$Block) 
biomass_ST_combine$Treatment <- as.factor(biomass_ST_combine$Treatment) 

aov.ST_weights <- aov(weight_per_plant ~ id + Block, data = biomass_ST_combine)

plot(aov.ST_weights)

summary(aov.ST_weights)
```

Can combine ST as p > 0.05

## C. virgata Analysis

### Run 1

```{r}
biomass_data_run1_FTR_weights$Block <- as.factor(biomass_data_run1_FTR_weights$Block) 
biomass_data_run1_FTR_weights$Treatment <- as.factor(biomass_data_run1_FTR_weights$Treatment) 

FTR_R1_aov <- aov(weight_per_plant ~ Treatment + Block, data = biomass_data_run1_FTR_weights)
```

```{r}
plot(FTR_R1_aov)

summary(FTR_R1_aov)
```

Posthoc

```{r}
FTR_R1_aov_tukey <- HSD.test(FTR_R1_aov, group = TRUE, trt = "Treatment")

FTR_R1_aov_tukey$groups
```

### Run 2

```{r}
biomass_data_run2_FTR_weights[is.na(biomass_data_run2_FTR_weights)] = 0

biomass_data_run2_FTR_weights$Block <- as.factor(biomass_data_run2_FTR_weights$Block) 
biomass_data_run2_FTR_weights$Treatment <- as.factor(biomass_data_run2_FTR_weights$Treatment) 

FTR_R2_aov <- aov(weight_per_plant ~ Treatment + Block, data = biomass_data_run2_FTR_weights)
```

```{r}
plot(FTR_R2_aov)

summary(FTR_R2_aov)
```

Posthoc

```{r}
FTR_R2_aov_tukey <- HSD.test(FTR_R2_aov, group = TRUE, trt = "Treatment")

FTR_R2_aov_tukey$groups
```

## S. oleraceus Analysis

### Run 1

```{r}
biomass_data_run1_ST_weights[is.na(biomass_data_run1_ST_weights)] = 0

biomass_data_run1_ST_weights$Block <- as.factor(biomass_data_run1_ST_weights$Block) 
biomass_data_run1_ST_weights$Treatment <- as.factor(biomass_data_run1_ST_weights$Treatment) 

ST_R1_aov <- aov(weight_per_plant ~ Treatment + Block, data = biomass_data_run1_ST_weights)
```

```{r}
plot(ST_R1_aov)

summary(ST_R1_aov)
```

Posthoc

```{r}
ST_R1_aov_tukey <- HSD.test(ST_R1_aov, group = TRUE, trt = "Treatment")

ST_R1_aov_tukey$groups
```

### Run 2

```{r}
biomass_data_run2_ST_weights[is.na(biomass_data_run2_ST_weights)] = 0
biomass_data_run2_ST_weights$Block <- as.factor(biomass_data_run2_ST_weights$Block) 
biomass_data_run2_ST_weights$Treatment <- as.factor(biomass_data_run2_ST_weights$Treatment) 

ST_R2_aov <- aov(weight_per_plant ~ Treatment + Block, data = biomass_data_run2_ST_weights)
```

```{r}
plot(ST_R2_aov)

summary(ST_R2_aov)
```

Posthoc

```{r}
ST_R2_aov_tukey <- HSD.test(ST_R2_aov, group = TRUE, trt = "Treatment")

ST_R2_aov_tukey$groups
```

## Conyza spp. Analysis

### Run 1

```{r}
biomass_data_run1_FB <- filter(biomass_data_run1, Species == "FB")

biomass_data_run1_FB_trim <- biomass_data_run1_FB[,-c(1, 3, 4, 5, 6, 9)]
biomass_data_run1_FB_trim <- biomass_data_run1_FB_trim[complete.cases(biomass_data_run1_FB$Weight),]

biomass_data_run1_FB_weights <- mutate(biomass_data_run1_FB_trim, weight_per_plant = (Weight/Number_surviving_after_28_days))

biomass_data_run1_FB_weights[is.na(biomass_data_run1_FB_weights)] = 0
```


```{r}
biomass_data_run1_FB_weights$Fleabane_block <- as.factor(biomass_data_run1_FB_weights$Fleabane_block) 
biomass_data_run1_FB_weights$Treatment <- as.factor(biomass_data_run1_FB_weights$Treatment) 

FB_R1_aov <- aov(weight_per_plant ~ Treatment + Fleabane_block, data = biomass_data_run1_FB_weights)
```

```{r}
plot(FB_R1_aov)

summary(FB_R1_aov)
```

Posthoc

```{r}
FB_R1_aov_tukey <- HSD.test(FB_R1_aov, group = TRUE, trt = "Treatment")

FB_R1_aov_tukey$groups
```

### Run 2

```{r}
biomass_data_run2_FB <- filter(biomass_data_run2_trim, Species == "FB")
biomass_data_run2_FB_weights <- mutate(biomass_data_run2_FB, weight_per_plant = (Weight/Number_surviving_after_28_days))
biomass_data_run2_FB_weights[is.na(biomass_data_run2_FB_weights)] = 0
```


```{r}
biomass_data_run2_FB_weights$Block <- as.factor(biomass_data_run2_FB_weights$Block) 
biomass_data_run2_FB_weights$Treatment <- as.factor(biomass_data_run2_FB_weights$Treatment) 

FB_R2_aov <- aov(weight_per_plant ~ Treatment + Block, data = biomass_data_run2_FB_weights)
```

```{r}
plot(FB_R2_aov)

summary(FB_R2_aov)
```

Posthoc

```{r}
FB_R2_aov_tukey <- HSD.test(FB_R2_aov, group = TRUE, trt = "Treatment")

FB_R2_aov_tukey$groups
```

# Visual Injury

```{r}
damage_data_run1 <- read_xlsx("damage_data.xlsx", sheet = "Run1")
damage_data_run2 <- read_xlsx("damage_data.xlsx", sheet = "Run2")
```

## Comparison between C. virgata Experiments

```{r}
damage_data_run1_trim <- damage_data_run1[,-c(1, 5)]
damage_data_run2_trim <- damage_data_run2[,-c(1)]
```

Selecting FTR rows

```{r}
damage_data_run1_FTR <- filter(damage_data_run1_trim, Species == "FTR")
damage_data_run2_FTR <- filter(damage_data_run2_trim, Species == "FTR")
```

Creating percent damage column

```{r}
damage_data_run1_FTR_percent <- mutate(damage_data_run1_FTR, percent_damage = (`Percent Plant Damage`/100))
damage_data_run2_FTR_percent <- mutate(damage_data_run2_FTR, percent_damage = (`Percent Plant Damage`/100))
```

Combining data sets

```{r}
damage_FTR_combine <- bind_rows(damage_data_run1_FTR_percent, damage_data_run2_FTR_percent, .id = "id")
```

T-test

```{r}
damage_FTR_combine$id <- as.factor(damage_FTR_combine$id) 
damage_FTR_combine$Block <- as.factor(damage_FTR_combine$Block) 
damage_FTR_combine$Treatment <- as.factor(damage_FTR_combine$Treatment) 
```

```{r}
vor_remove <- c("vor", "para/vor")

damage_FTR_combine_filter <- filter(damage_FTR_combine, !Treatment %in% vor_remove) #Removing voraxor involved treatments

glmer.FTR_percent <- glmer(percent_damage ~ id + (1|Block), family = binomial, data = damage_FTR_combine)
```

```{r}
summary(glmer.FTR_percent)
```

## Comparison between S. oleraceus Experiments

```{r}
damage_data_run1_trim <- damage_data_run1[,-c(1, 5)]
damage_data_run2_trim <- damage_data_run2[,-c(1)]
```

Selecting ST rows

```{r}
damage_data_run1_ST <- filter(damage_data_run1_trim, Species == "ST")
damage_data_run2_ST <- filter(damage_data_run2_trim, Species == "ST")
```

Creating weight/surviving plants column

```{r}
damage_data_run1_ST_percent <- mutate(damage_data_run1_ST, percent_damage = (`Percent Plant Damage`/100))
damage_data_run2_ST_percent <- mutate(damage_data_run2_ST, percent_damage = (`Percent Plant Damage`/100))
```

Combining data sets

```{r}
damage_ST_combine <- bind_rows(damage_data_run1_ST_percent, damage_data_run2_ST_percent, .id = "id")
```

T-test

```{r}
damage_ST_combine$id <- as.factor(damage_ST_combine$id) 
damage_ST_combine$Block <- as.factor(damage_ST_combine$Block) 
damage_ST_combine$Treatment <- as.factor(damage_ST_combine$Treatment) 
```

```{r}
glmer.ST_percent <- glmer(percent_damage ~ id + (1|Block), family = binomial, data = damage_ST_combine)
```

```{r}
summary(glmer.ST_percent)
```

## C. virgata Analysis

### Run 1

```{r}
damage_data_run1_FTR_percent_clean <- damage_data_run1_FTR_percent[complete.cases(damage_data_run1_FTR_percent),]

damage_data_run1_FTR_percent_clean$Day <- as.factor(damage_data_run1_FTR_percent_clean$Day) 
damage_data_run1_FTR_percent_clean$Treatment <- as.factor(damage_data_run1_FTR_percent_clean$Treatment)
damage_data_run1_FTR_percent_clean$Block <- as.factor(damage_data_run1_FTR_percent_clean$Block)
```


```{r}
damage_data_run1_FTR_percent_clean <- mutate(damage_data_run1_FTR_percent_clean, asin_percent_damage = (asin(sqrt(percent_damage))))

cs1<-corCompSymm(0.5,form=~1|Block)
gls.FTR_R1_percent <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs1, data = damage_data_run1_FTR_percent_clean)
vfc2<-varIdent(form=~1|Day)
cs2<-corCompSymm(0.5,form=~1|Block)
gls.FTR_R2_percent <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs2, weights = vfc2, data = damage_data_run1_FTR_percent_clean)
cs3 <- corCAR1(form=~1|Block)
gls.FTR_R3_percent <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs3, data = damage_data_run1_FTR_percent_clean)
vfc4<-varIdent(form=~1|Day)
cs4<-corCAR1(form=~1|Block)
gls.FTR_R4_percent <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs4, weights = vfc4, data = damage_data_run1_FTR_percent_clean)

AIC(gls.FTR_R1_percent)
AIC(gls.FTR_R2_percent)
AIC(gls.FTR_R3_percent)
AIC(gls.FTR_R4_percent)

# R2 model has the lowest AIC

plot(gls.FTR_R2_percent)

Anova(gls.FTR_R2_percent) # interaction is significant

anova(gls.FTR_R2_percent)

emm.FTR_R2_percent <- emmeans(gls.FTR_R2_percent, specs = pairwise ~ Treatment|Day)

cld(emm.FTR_R2_percent)
```

Back-transformed means

```{r}
avg_asin_FTR_R1 <- damage_data_run1_FTR_percent_clean %>%
  group_by(Day) %>%
  group_by(Treatment, .add = TRUE) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_asin_FTR_R1 <- mutate(avg_asin_FTR_R1, mean_asin_backtrans = ((sin(mean_asin))^2))

avg_asin_FTR_R1
```

### Run 2

```{r}
damage_data_run2_FTR_percent_clean <- damage_data_run2_FTR_percent[complete.cases(damage_data_run2_FTR_percent),]

damage_data_run2_FTR_percent_clean$Day <- as.factor(damage_data_run2_FTR_percent_clean$Day) 
damage_data_run2_FTR_percent_clean$Treatment <- as.factor(damage_data_run2_FTR_percent_clean$Treatment)
damage_data_run2_FTR_percent_clean$Block <- as.factor(damage_data_run2_FTR_percent_clean$Block)
```

```{r}
damage_data_run2_FTR_percent_clean <- mutate(damage_data_run2_FTR_percent_clean, asin_percent_damage = (asin(sqrt(percent_damage))))

cs1<-corCompSymm(0.5,form=~1|Block)
gls.FTR_R2_percent_M1 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs1, data = damage_data_run2_FTR_percent_clean)
vfc2<-varIdent(form=~1|Day)
cs2<-corCompSymm(0.5,form=~1|Block)
gls.FTR_R2_percent_M2 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs2, weights = vfc2, data = damage_data_run2_FTR_percent_clean)
cs3 <- corCAR1(form=~1|Block)
gls.FTR_R2_percent_M3 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs3, data = damage_data_run2_FTR_percent_clean)
vfc4<-varIdent(form=~1|Day)
cs4<-corCAR1(form=~1|Block)
gls.FTR_R2_percent_M4 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs4, weights = vfc4, data = damage_data_run2_FTR_percent_clean)

AIC(gls.FTR_R2_percent_M1)
AIC(gls.FTR_R2_percent_M2)
AIC(gls.FTR_R2_percent_M3)
AIC(gls.FTR_R2_percent_M4)

# M2 has the lowest AIC

plot(gls.FTR_R2_percent)

Anova(gls.FTR_R2_percent_M2) # interaction is significant

emm.FTR_R2_percent_M2 <- emmeans(gls.FTR_R2_percent_M2, specs = pairwise ~ Treatment|Day)

cld(emm.FTR_R2_percent_M2)
```

Backtransformed means

```{r}
avg_asin_FTR_R2 <- damage_data_run2_FTR_percent_clean %>%
  group_by(Day) %>%
  group_by(Treatment, .add = TRUE) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_asin_FTR_R2 <- mutate(avg_asin_FTR_R2, mean_asin_backtrans = ((sin(mean_asin))^2))
```

## S. oleraceus Analysis

### Run 1

```{r}
damage_data_run1_ST_percent_clean <- damage_data_run1_ST_percent[complete.cases(damage_data_run1_ST_percent),]

damage_data_run1_ST_percent_clean$Day <- as.factor(damage_data_run1_ST_percent_clean$Day) 
damage_data_run1_ST_percent_clean$Treatment <- as.factor(damage_data_run1_ST_percent_clean$Treatment)
damage_data_run1_ST_percent_clean$Block <- as.factor(damage_data_run1_ST_percent_clean$Block)
```

```{r}
damage_data_run1_ST_percent_clean <- mutate(damage_data_run1_ST_percent_clean, asin_percent_damage = (asin(sqrt(percent_damage))))

cs1<-corCompSymm(0.5,form=~1|Block)
gls.run1_ST_percent_M1 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs1, data = damage_data_run1_ST_percent_clean)
vfc2<-varIdent(form=~1|Day)
cs2<-corCompSymm(0.5,form=~1|Block)
gls.run1_ST_percent_M2 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs2, weights = vfc2, data = damage_data_run1_ST_percent_clean)
cs3 <- corCAR1(form=~1|Block)
gls.run1_ST_percent_M3 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs3, data = damage_data_run1_ST_percent_clean)
vfc4<-varIdent(form=~1|Day)
cs4<-corCAR1(form=~1|Block)
gls.run1_ST_percent_M4 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs4, weights = vfc4, data = damage_data_run1_ST_percent_clean)

AIC(gls.run1_ST_percent_M1)
AIC(gls.run1_ST_percent_M2)
AIC(gls.run1_ST_percent_M3)
AIC(gls.run1_ST_percent_M4)

# M2 has the lowest AIC

plot(gls.run1_ST_percent_M2) # Fanning accounted for in weighted variance structure

Anova(gls.run1_ST_percent_M2) # interaction is significant

plot(gls.run1_ST_percent_M2)

emm.run1_ST_percent_M2 <- emmeans(gls.run1_ST_percent_M2, specs = pairwise ~ Treatment|Day)

cld(emm.run1_ST_percent_M2)
```

Backtransformed means

```{r}
avg_asin_ST_R1 <- damage_data_run1_ST_percent_clean %>%
  group_by(Day) %>%
  group_by(Treatment, .add = TRUE) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_asin_ST_R1 <- mutate(avg_asin_ST_R1, mean_asin_backtrans = ((sin(mean_asin))^2))

avg_asin_ST_R1
```

### Run 2

```{r}
damage_data_run2_ST_percent_clean <- damage_data_run2_ST_percent[complete.cases(damage_data_run2_ST_percent),]

damage_data_run2_ST_percent_clean$Day <- as.factor(damage_data_run2_ST_percent_clean$Day) 
damage_data_run2_ST_percent_clean$Treatment <- as.factor(damage_data_run2_ST_percent_clean$Treatment)
damage_data_run2_ST_percent_clean$Block <- as.factor(damage_data_run2_ST_percent_clean$Block)
```

```{r}
damage_data_run2_ST_percent_clean <- mutate(damage_data_run2_ST_percent_clean, asin_percent_damage = (asin(sqrt(percent_damage))))

cs1<-corCompSymm(0.5,form=~1|Block)
gls.run2_ST_percent_M1 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs1, data = damage_data_run2_ST_percent_clean)
vfc2<-varIdent(form=~1|Day)
cs2<-corCompSymm(0.5,form=~1|Block)
gls.run2_ST_percent_M2 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs2, weights = vfc2, data = damage_data_run2_ST_percent_clean)
cs3 <- corCAR1(form=~1|Block)
gls.run2_ST_percent_M3 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs3, data = damage_data_run2_ST_percent_clean)
vfc4<-varIdent(form=~1|Day)
cs4<-corCAR1(form=~1|Block)
gls.run2_ST_percent_M4 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs4, weights = vfc4, data = damage_data_run2_ST_percent_clean)

AIC(gls.run2_ST_percent_M1)
AIC(gls.run2_ST_percent_M2)
AIC(gls.run2_ST_percent_M3)
AIC(gls.run2_ST_percent_M4)

# M2 has lowest AIC

plot(gls.run2_ST_percent_M2)

Anova(gls.run2_ST_percent_M2) # interaction is significant

emm.run2_ST_percent_M2 <- emmeans(gls.run2_ST_percent_M2, specs = pairwise ~ Treatment|Day)

cld(emm.run2_ST_percent_M2)
```

Backtransformed means

```{r}
avg_asin_ST_R2 <- damage_data_run2_ST_percent_clean %>%
  group_by(Day) %>%
  group_by(Treatment, .add = TRUE) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_asin_ST_R2 <- mutate(avg_asin_ST_R2, mean_asin_backtrans = ((sin(mean_asin))^2))

avg_asin_ST_R2
```

## Conyza spp. Analysis

### Run 1

```{r}
damage_data_run1_FB <- filter(damage_data_run1_trim, Species == "FB")
damage_data_run1_FB_percent <- mutate(damage_data_run1_FB, percent_damage = (`Percent Plant Damage`/100))
```

```{r}
damage_data_run1_FB_percent_clean <- damage_data_run1_FB_percent[complete.cases(damage_data_run1_FB_percent),]

damage_data_run1_FB_percent_clean$Day <- as.factor(damage_data_run1_FB_percent_clean$Day) 
damage_data_run1_FB_percent_clean$Treatment <- as.factor(damage_data_run1_FB_percent_clean$Treatment)
damage_data_run1_FB_percent_clean$Block <- as.factor(damage_data_run1_FB_percent_clean$Block)
```

```{r}
damage_data_run1_FB_percent_clean <- mutate(damage_data_run1_FB_percent_clean, asin_percent_damage = (asin(sqrt(percent_damage))))

damage_data_run1_FB_percent_clean <- mutate(damage_data_run1_FB_percent_clean, asin_backtrans_percent_damage = ((sin(asin_percent_damage))^2))

cs1<-corCompSymm(0.5,form=~1|Block)
gls.run1_FB_percent_M1 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs1, data = damage_data_run1_FB_percent_clean)
vfc2<-varIdent(form=~1|Day)
cs2<-corCompSymm(0.5,form=~1|Block)
gls.run1_FB_percent_M2 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs2, weights = vfc2, data = damage_data_run1_FB_percent_clean)
cs3 <- corCAR1(form=~1|Block)
gls.run1_FB_percent_M3 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs3, data = damage_data_run1_FB_percent_clean)
vfc4<-varIdent(form=~1|Day)
cs4<-corCAR1(form=~1|Block)
gls.run1_FB_percent_M4 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs4, weights = vfc4, data = damage_data_run1_FB_percent_clean)

AIC(gls.run1_FB_percent_M1)
AIC(gls.run1_FB_percent_M2)
AIC(gls.run1_FB_percent_M3)
AIC(gls.run1_FB_percent_M4)

# M2 has lowest AIC

plot(gls.run1_FB_percent_M2) # Fanning accounted for in weighted variance structure

Anova(gls.run1_FB_percent_M2) # interaction is significant

emm.run1_FB_percent_M2 <- emmeans(gls.run1_FB_percent_M2, specs = pairwise ~ Treatment|Day)

cld(emm.run1_FB_percent_M2)
```

```{r}
avg_asin_FB_R1 <- damage_data_run1_FB_percent_clean %>%
  group_by(Day) %>%
  group_by(Treatment, .add = TRUE) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_asin_FB_R1 <- mutate(avg_asin_FB_R1, mean_asin_backtrans = ((sin(mean_asin))^2))

avg_asin_FB_R1
```

### Run 2

```{r}
damage_data_run2_FB <- filter(damage_data_run2_trim, Species == "FB")
damage_data_run2_FB_percent <- mutate(damage_data_run2_FB, percent_damage = (`Percent Plant Damage`/100))
```

```{r}
damage_data_run2_FB_percent_clean <- damage_data_run2_FB_percent[complete.cases(damage_data_run2_FB_percent),]

damage_data_run2_FB_percent_clean$Day <- as.factor(damage_data_run2_FB_percent_clean$Day) 
damage_data_run2_FB_percent_clean$Treatment <- as.factor(damage_data_run2_FB_percent_clean$Treatment)
damage_data_run2_FB_percent_clean$Block <- as.factor(damage_data_run2_FB_percent_clean$Block)
```

```{r}
damage_data_run2_FB_percent_clean <- mutate(damage_data_run2_FB_percent_clean, asin_percent_damage = (asin(sqrt(percent_damage))))

avg_asin_FB_R2 <- damage_data_run2_FB_percent_clean %>%
  group_by(Day) %>%
  group_by(Treatment, .add = TRUE) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_asin_FB_R2 <- mutate(avg_asin_FB_R2, mean_asin_backtrans = ((sin(mean_asin))^2))

cs1<-corCompSymm(0.5,form=~1|Block)
gls.run2_FB_percent_M1 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs1, data = damage_data_run2_FB_percent_clean)
vfc2<-varIdent(form=~1|Day)
cs2<-corCompSymm(0.5,form=~1|Block)
gls.run2_FB_percent_M2 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs2, weights = vfc2, data = damage_data_run2_FB_percent_clean)
cs3 <- corCAR1(form=~1|Block)
gls.run2_FB_percent_M3 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs3, data = damage_data_run2_FB_percent_clean)
vfc4<-varIdent(form=~1|Day)
cs4<-corCAR1(form=~1|Block)
gls.run2_FB_percent_M4 <- gls(asin_percent_damage ~ Treatment*Day, correlation = cs4, weights = vfc4, data = damage_data_run2_FB_percent_clean)

AIC(gls.run2_FB_percent_M1)
AIC(gls.run2_FB_percent_M2)
AIC(gls.run2_FB_percent_M3)
AIC(gls.run2_FB_percent_M4)

# M2 has the lowest AIC

plot(gls.run2_FB_percent_M2) # Fanning accounted for in weighted variance structure

Anova(gls.run2_FB_percent_M2) # interaction is significant

emm.run2_FB_percent_M2 <- emmeans(gls.run2_FB_percent_M2, specs = pairwise ~Treatment|Day)

cld(emm.run2_FB_percent_M2)
```

Backtransformed means

```{r}
avg_asin_FB_R2 <- damage_data_run2_FB_percent_clean %>%
  group_by(Day) %>%
  group_by(Treatment, .add = TRUE) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_asin_FB_R2 <- mutate(avg_asin_FB_R2, mean_asin_backtrans = ((sin(mean_asin))^2))

avg_asin_FB_R2
```



