---
title: "Looking Beyond Glyphosate for Site-Specific Weed Control"
author: '490416255'
output:
  html_document:
    code_folding:
    fig_caption: yes
    number_sections: yes
    self_contained: yes
    theme: journal
    toc: yes
    toc_depth: 3
    toc_float: yes
  word_document:
    toc: yes
    toc_depth: '3'
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r include = FALSE}
require(dplyr)
require(ggplot2)
require(readxl)
require(agricolae)
require(emmeans)
require(lattice)
require(lme4)
require(nlme)
require(car)
require(glmmTMB)
require(brms)
require(rms)
require(broom.mixed)
require(multcomp)
require(multcompView)
require(MASS)
require(olsrr)
```

# Plant Survival

```{r}
biomass_data_run1 <- read_xlsx("biomass_data.xlsx", sheet = "Run1")
biomass_data_run2 <- read_xlsx("biomass_data.xlsx", sheet = "Run2")
```

## Comparison between C. virgata Experiments

```{r}
biomass_data_run1_trim <- biomass_data_run1[,-c(1, 2, 4, 6, 10)]
biomass_data_run2_trim <- biomass_data_run2[,-c(1, 2, 4, 6, 8)]
```

Selecting FTR rows

```{r}
biomass_data_run1_FTR <- filter(biomass_data_run1_trim, Species == "FTR")
biomass_data_run2_FTR <- filter(biomass_data_run2_trim, Species == "FTR")
```

Creating survival column

```{r}
biomass_data_run1_FTR_survival <- mutate(biomass_data_run1_FTR, survival = ((Number_surviving_after_28_days/Plant_Number)))

biomass_data_run2_FTR_survival <- mutate(biomass_data_run2_FTR, survival = ((Number_surviving_after_28_days/Plant_Number)))
```

Combining data sets

```{r}
survival_FTR_combine <- bind_rows(biomass_data_run1_FTR_survival, biomass_data_run2_FTR_survival, .id = "id")
```

```{r}
survival_FTR_combine$id <- as.factor(survival_FTR_combine$id) 
survival_FTR_combine$Block <- as.factor(survival_FTR_combine$Block) 
survival_FTR_combine$Treatment <- as.factor(survival_FTR_combine$Treatment) 
```

```{r}
vor_remove <- c("vor", "para/vor") #Remove voraxor involved treatments

survival_FTR_combine_filter <- filter(survival_FTR_combine, !Treatment %in% vor_remove)

glmer.FTR_survival <- glmer(survival ~ id + (1|Block), family = binomial, data = survival_FTR_combine_filter)
summary(glmer.FTR_survival)
```

Can't combine as p < 0.05

## Comparison between S. oleraceus Experiments

Selecting ST rows

```{r}
biomass_data_run1_ST <- filter(biomass_data_run1_trim, Species == "ST")
biomass_data_run2_ST <- filter(biomass_data_run2_trim, Species == "ST")
```

Creating survival column

```{r}
biomass_data_run1_ST_survival <- mutate(biomass_data_run1_ST, survival = ((Number_surviving_after_28_days/Plant_Number)))

biomass_data_run2_ST_survival <- mutate(biomass_data_run2_ST, survival = ((Number_surviving_after_28_days/Plant_Number)))
```

Combining data sets

```{r}
survival_ST_combine <- bind_rows(biomass_data_run1_ST_survival, biomass_data_run2_ST_survival, .id = "id")
```

```{r}
survival_ST_combine$id <- as.factor(survival_ST_combine$id) 
survival_ST_combine$Block <- as.factor(survival_ST_combine$Block) 
survival_ST_combine$Treatment <- as.factor(survival_ST_combine$Treatment) 
```

```{r}
glmer.ST_survival <- glmer(survival ~ id + (1|Block), family = binomial, data = survival_ST_combine)
summary(glmer.ST_survival)
```

Can't combine as p < 0.05

## C. virgata Analysis

### Run 1

Generalised least squares regression

```{r}
biomass_data_run1_FTR_survival <- mutate(biomass_data_run1_FTR_survival, asin_percent_damage = (asin(sqrt(survival))))

biomass_data_run1_FTR_survival <- mutate(biomass_data_run1_FTR_survival, asin_backtrans_percent_damage = ((sin(asin_percent_damage))^2))

gls.FTR_R1_survival_M1 <- gls(asin_percent_damage ~ Treatment + Block, data = biomass_data_run1_FTR_survival)

plot(gls.FTR_R1_survival_M1) # Fanning residuals - model assumptions were not met
```

Backtranformed means

```{r}
avg_asin_FTR_R1_survival <- biomass_data_run1_FTR_survival %>%
  group_by(Treatment) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_sin_FTR_R1_survival <- mutate(avg_asin_FTR_R1_survival, mean_asin_backtrans = ((sin(mean_asin))^2))

avg_sin_FTR_R1_survival
```

### Run 2

```{r}
biomass_data_run2_FTR_survival$Treatment <- as.factor(biomass_data_run2_FTR_survival$Treatment) 
biomass_data_run2_FTR_survival$Block <- as.factor(biomass_data_run2_FTR_survival$Block)
```

```{r}
biomass_data_run2_FTR_survival <- mutate(biomass_data_run2_FTR_survival, asin_percent_damage = (asin(sqrt(survival))))

biomass_data_run2_FTR_survival <- mutate(biomass_data_run2_FTR_survival, asin_backtrans_percent_damage = ((sin(asin_percent_damage))^2))

gls.FTR_R2_survival <- gls(asin_percent_damage ~ Treatment + Block, data = biomass_data_run2_FTR_survival)

plot(gls.FTR_R2_survival)

Anova(gls.FTR_R2_survival)

emm.FTR_R2_Survival <- emmeans(gls.FTR_R2_survival, specs = ~ Treatment)

cld(emm.FTR_R2_Survival) 
```

Backtransformed means

```{r}
avg_asin_FTR_R2_survival <- biomass_data_run2_FTR_survival %>%
  group_by(Treatment) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_sin_FTR_R2_survival <- mutate(avg_asin_FTR_R2_survival, mean_asin_backtrans = ((sin(mean_asin))^2))

avg_sin_FTR_R2_survival
```


## S. oleraceus Analysis

### Run 1

```{r}
biomass_data_run1_ST_survival <- mutate(biomass_data_run1_ST_survival, asin_percent_damage = (asin(sqrt(survival))))

biomass_data_run1_ST_survival <- mutate(biomass_data_run1_ST_survival, asin_backtrans_percent_damage = ((sin(asin_percent_damage))^2))

gls.ST_R1_survival <- gls(asin_percent_damage ~ Treatment + Block, data = biomass_data_run1_ST_survival)

plot(gls.ST_R1_survival)

Anova(gls.ST_R1_survival)

emm.ST_R1_Survival <- emmeans(gls.ST_R1_survival, specs = ~ Treatment)

cld(emm.ST_R1_Survival) 
```

```{r}
avg_asin_ST_R1_survival <- biomass_data_run1_ST_survival %>%
  group_by(Treatment) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_sin_ST_R1_survival <- mutate(avg_asin_ST_R1_survival, mean_asin_backtrans = ((sin(mean_asin))^2))

avg_sin_ST_R1_survival
```

### Run 2

```{r}
biomass_data_run2_ST_survival$Treatment <- as.factor(biomass_data_run2_ST_survival$Treatment) 
biomass_data_run2_ST_survival$Block <- as.factor(biomass_data_run2_ST_survival$Block)
```

```{r}
biomass_data_run2_ST_survival <- mutate(biomass_data_run2_ST_survival, asin_percent_damage = (asin(sqrt(survival))))

biomass_data_run2_ST_survival <- mutate(biomass_data_run2_ST_survival, asin_backtrans_percent_damage = ((sin(asin_percent_damage))^2))

gls.ST_R2_survival <- gls(asin_percent_damage ~ Treatment + Block, data = biomass_data_run2_ST_survival)

plot(gls.ST_R2_survival)

Anova(gls.ST_R2_survival)

emm.ST_R2_Survival <- emmeans(gls.ST_R2_survival, specs = ~ Treatment)

cld(emm.ST_R2_Survival) 
```

```{r}
avg_asin_ST_R2_survival <- biomass_data_run2_ST_survival %>%
  group_by(Treatment) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_sin_ST_R2_survival <- mutate(avg_asin_ST_R2_survival, mean_asin_backtrans = ((sin(mean_asin))^2))
```


## Conyza spp. R1 Analysis

```{r}
biomass_data_run1_FB <- filter(biomass_data_run1_trim, Species == "FB")
biomass_data_run1_FB_survival <- mutate(biomass_data_run1_FB, survival = ((Number_surviving_after_28_days/Plant_Number)))
biomass_data_run1_FB_survival_clean <- biomass_data_run1_FB_survival[complete.cases(biomass_data_run1_FB_survival),]
```

```{r}
biomass_data_run1_FB_survival_clean_asin <- mutate(biomass_data_run1_FB_survival_clean, asin_percent_damage=(asin(sqrt(survival))))

gls.FB_R1_survival <- gls(asin_percent_damage ~ Treatment + Block, data = biomass_data_run1_FB_survival_clean_asin)

plot(gls.FB_R1_survival)

Anova(gls.FB_R1_survival)

emm.FB_R1_Survival <- emmeans(gls.FB_R1_survival, specs = ~ Treatment)

cld(emm.FB_R1_Survival) 
```

```{r}
avg_asin_FB_R1_survival <- biomass_data_run1_FB_survival_clean_asin %>%
  group_by(Treatment) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_sin_FB_R1_survival <- mutate(avg_asin_FB_R1_survival, mean_asin_backtrans = ((sin(mean_asin))^2))

avg_sin_FB_R1_survival
```


## Conyza spp. R2 Analysis

```{r}
biomass_data_run2_FB <- filter(biomass_data_run2_trim, Species == "FB")
biomass_data_run2_FB_survival <- mutate(biomass_data_run2_FB, survival = ((Number_surviving_after_28_days/Plant_Number)))
```

```{r}
biomass_data_run2_FB_survival <- mutate(biomass_data_run2_FB_survival, asin_percent_damage = (asin(sqrt(survival))))

gls.FB_R2_survival <- gls(asin_percent_damage ~ Treatment + Block, data = biomass_data_run2_FB_survival)

plot(gls.FB_R2_survival)

Anova(gls.FB_R2_survival)

emm.FB_R2_Survival <- emmeans(gls.FB_R2_survival, specs = ~ Treatment)

cld(emm.FB_R2_Survival) 
```

```{r}
avg_asin_FB_R2_survival <- biomass_data_run2_FB_survival %>%
  group_by(Treatment) %>%
  summarise(mean_asin = mean(asin_percent_damage))

avg_sin_FB_R2_survival <- mutate(avg_asin_FB_R2_survival, mean_asin_backtrans = ((sin(mean_asin))^2))

avg_sin_FB_R2_survival
```